---
title: "quantileMapping_05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

this is for comparing quantile differences (percent vs #) in sim 

## LOAD DATA ##
```{r}
mauDataRsp  <- read.table("dmau_x_rsp_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
melDataRsp  <- read.table("dmel_x_rsp_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
simDataRsp  <- read.table("dsim_x_rsp_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
sechDataRsp <- read.table("dsech_x_rsp_q1_q1_f4_03.tsv", header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 

mauData1.688  <- read.table("dmau_x_1.688_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
melData1.688  <- read.table("dmel_x_1.688_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
simData1.688  <- read.table("dsim_x_1.688_q1_q1_f4_03.tsv",  header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
sechData1.688 <- read.table("dsech_x_1.688_q1_q1_f4_03.tsv", header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE) 
```

Add a lower estimate of maxDy since NaNs are included
```{r}
addMaxDy <- function(df){
  df$maxDyLowerEst <- pmax(
  abs(df$first.middle - df$middle.middle),
  abs(df$middle.last - df$middle.middle),
  na.rm = TRUE
)
  return(df)
}
```

```{r}
mauData1.688 <- addMaxDy(mauData1.688)
melData1.688 <- addMaxDy(melData1.688)
simData1.688 <- addMaxDy(simData1.688)
sechData1.688 <- addMaxDy(sechData1.688)

mauDataRsp <- addMaxDy(mauDataRsp)
melDataRsp <- addMaxDy(melDataRsp)
simDataRsp <- addMaxDy(simDataRsp)
sechDataRsp <- addMaxDy(sechDataRsp)
```

```{r}
write.csv(mauData1.688, "mauData1.688.csv")
write.csv(melData1.688, "melData1.688.csv")
write.csv(simData1.688, "simData1.688.csv")
write.csv(sechData1.688, "sechData1.688.csv")

write.csv(mauDataRsp, "mauDataRsp.csv")
write.csv(melDataRsp, "melDataRsp.csv")
write.csv(simDataRsp, "simDataRsp.csv")
write.csv(sechDataRsp, "sechDataRsp.csv")
```

```{r}
boxplot(melDataRsp$maxDyLowerEst, melData1.688$maxDyLowerEst,mauDataRsp$maxDyLowerEst, mauData1.688$maxDyLowerEst, simDataRsp$maxDyLowerEst, simData1.688$maxDyLowerEst, sechDataRsp$maxDyLowerEst, sechData1.688$maxDyLowerEst, names=c("mel Rsp", "mel 1.688", "mau rsp", "mau 1.688", "sim rsp", "sim 1.688", "sech rsp", "sech 1.688"), col=c("blue", "darkgreen"), ylab="max dy, lower estimate")
```



## TRIM DATA##
### only use this trim when plotting the line plots , do not use for heatmap###
```{r}
mauDataRsp  <- rbind(mauDataRsp[1,],   mauDataRsp[complete.cases(mauDataRsp), ])
melDataRsp  <- rbind(melDataRsp[1,],   melDataRsp[complete.cases(melDataRsp), ])
simDataRsp  <- rbind(simDataRsp[1,],   simDataRsp[complete.cases(simDataRsp), ])
sechDataRsp <- rbind(sechDataRsp[1,], sechDataRsp[complete.cases(sechDataRsp), ])

mauData1.688  <- rbind(mauData1.688[1,],   mauData1.688[complete.cases(mauData1.688), ])
melData1.688  <- rbind(melData1.688[1,],   melData1.688[complete.cases(melData1.688), ])
simData1.688  <- rbind(simData1.688[1,],   simData1.688[complete.cases(simData1.688), ])
sechData1.688 <- rbind(sechData1.688[1,], sechData1.688[complete.cases(sechData1.688), ])
```



## PLOTTING FUNCTIONS ##
```{r}
library(ggplot2)
library(cowplot)
library(reshape2)
library(shadowtext)

plotGridGrid2 <- function(dat1, name1, dat2, name2, dat3, name3, dat4, name4, c1 = "#003153", c2 = "deepskyblue"){
  dat1 <- round(colMeans(dat1[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat2 <- round(colMeans(dat2[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat3 <- round(colMeans(dat3[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat4 <- round(colMeans(dat4[-c(1), c(1:9)], na.rm = TRUE), 4)
  
  from <- c(rep("first", 3), rep("middle", 3), rep("last", 3))
  to <- c(rep(c("first", "middle", "last"), 3))
  
  rng <- range(dat1, dat2, dat3, dat4)
  
  lab <- "genetic\ndistance"
  
  tempavg1 <- matrix(dat1, nrow=9, byrow=TRUE)
  avg1 <- data.frame(tempavg1)
  colnames(avg1) <- "gen"
  avg1$from <- from
  avg1$to <- to
  
  tempavg2 <- matrix(dat2, nrow=9, byrow=TRUE)
  avg2 <- data.frame(tempavg2)
  colnames(avg2) <- "gen"
  avg2$from <- from
  avg2$to <- to
  
  tempavg3 <- matrix(dat3, nrow=9, byrow=TRUE)
  avg3 <- data.frame(tempavg3)
  colnames(avg3) <- "gen"
  avg3$from <- from
  avg3$to <- to
  
  tempavg4 <- matrix(dat4, nrow=9, byrow=TRUE)
  avg4 <- data.frame(tempavg4)
  colnames(avg4) <- "gen"
  avg4$from <- from
  avg4$to <- to
  
  color1 <- "#003153"
  color2 <- "deepskyblue"
  cc <- c(color1, color2)
  f <- 6
  
  q <- ggplot(data = avg1, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name1) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
  
  w <- ggplot(data = avg2, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name2) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
   
  e <- ggplot(data = avg3, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name3) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
  
   r <- ggplot(data = avg4, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name4) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
   
  tiff("Plot1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(q)
  dev.off()
  
  tiff("Plot1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(w)
  dev.off()
  
  tiff("Plot1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(e)
  dev.off()
  
  tiff("Plot1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(r)
  dev.off()
  
}

plotGrid <- function(dat, name){
  dat$band <- NULL
  tempdata <- round(dat, 4)
  title <- name
  avgmat <- matrix(tempdata[1,1:9], nrow=3, byrow=TRUE)
  from <- c(rep("first", 3), rep("middle", 3), rep("last", 3))
  to <- c(rep(c("first", "middle", "last"), 3))
  avg <- data.frame(as.numeric(tempdata[1,1:9]))
  colnames(avg) <- "gen"
  avg$from <- from
  avg$to <- to
  ggplot(data = avg, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) + 
    geom_tile() +
    geom_text(aes(from, to, label = gen), color = "black", size = 4) +
    ggtitle(title)
  cow1 <- ggplot(data = avg, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) + 
    geom_tile() +
    geom_text(aes(from, to, label = gen), color = "black", size = 4) +
    ggtitle(title)
  return(cow1)
}

plotGridGrid <- function(c1, c2, c3, c4){
  plot_grid(c1, c2, c3, c4, labels = NULL)
}


plotAllComparisons <- function(dat, name, xl = c(0.9, 7.5), yl=c(0,.21)){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  #ylim = c(0,1.1*max(data2[,-c(10,11)]))
  plot(x=NULL, xlim=xl, ylim = yl, xaxt='n', ylab="genetic distance", main = title)
  
  with(data2, symbols(x=rep(1,n)+j, y=data2$first.first, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc, add=TRUE))
  
  with(data2, symbols(x=rep(2,n)+j, y=data2$first.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(1,n)+j, y0=data2$first.first, x1=rep(2,n)+j, y1=data2$first.middle)
  
  with(data2, symbols(x=rep(3,n)+j, y=data2$first.last, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(2,n)+j, y0=data2$first.middle, x1=rep(3,n)+j, y1=data2$first.last)
  
  with(data2, symbols(x=rep(4,n)+j, y=data2$middle.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(3,n)+j, y0=data2$first.last, x1=rep(4,n)+j, y1=data2$middle.middle)
  
  with(data2, symbols(x=rep(5,n)+j, y=data2$middle.last, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(4,n)+j, y0=data2$middle.middle, x1=rep(5,n)+j, y1=data2$middle.last)
  
  with(data2, symbols(x=rep(6,n)+j, y=data2$last.last, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(5,n)+j, y0=data2$middle.last, x1=rep(6,n)+j, y1=data2$last.last)
  
  #legend("topright", legend=c("1: first.first" ,"2: first.middle" ,"3: first.last","4: middle.middle" ,"5: middle.last" ,  "6: last.last"  ), lty=1:2, cex=0.8, bg="transparent")
  axis(side=1, at=1:6, labels = c("1: first.first" ,"2: first.middle" ,"3: first.last","4: middle.middle" ,"5: middle.last" ,  "6: last.last"  ), las=0)
  ccc <- seq(1, n, 10)
  #legend(x=6.5, y=yl[2], legend=data2$band[ccc], col=cc[ccc], lty=1, lwd=9, cex=.6)
}


plotThreeComparisons <- function(dat, name, xl = c(0.9, 4), yl=c(0,.21)){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  #ylim = c(0,1.1*max(data2[,-c(10,11)]))
  plot(x=NULL, xlim=xl, ylim = yl, xaxt='n', ylab="genetic distance", main = title)
  
  with(data2, symbols(x=rep(1,n)+j, y=data2$first.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc, add=TRUE))
  
  with(data2, symbols(x=rep(2,n)+j, y=data2$middle.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(1,n)+j, y0=data2$first.middle, x1=rep(2,n)+j, y1=data2$middle.middle)
  
  with(data2, symbols(x=rep(3,n)+j, y=data2$last.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(2,n)+j, y0=data2$middle.middle, x1=rep(3,n)+j, y1=data2$last.middle)
  #legend("topright", legend=c("1: first.first" ,"2: first.middle" ,"3: first.last","4: middle.middle" ,"5: middle.last" ,  "6: last.last"  ), lty=1:2, cex=0.8, bg="transparent")
  axis(side=1, at=1:3, labels = c("1: first.middle" ,"2: middle.middle" ,"3: middle.last"), las=0)
  legend(x=3.5, y=yl[2],legend=data2$band, col=cc, lty=1, lwd=9, cex=.6)
}

plotdyhist <- function(xlim, dat, name){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  for(i in 1:n){
    data2$maxdy[i] <- max(abs(data2$first.middle[i] - data2$middle.middle[i]), abs(data2$middle.middle[i] - data2$middle.last[i]))
  }
  hist(data2$maxd, main=name, col="gray90", xlim = xlim, xlab=paste("max(|dy|)   n =", n))
}

plotdyhists <- function(xlim, dat1, name1, dat2, name2, dat3, name3, dat4, name4, parmf = c(2,2)){
  par(mfrow=parmf)
  plotdyhist(xlim, dat1, name1)
  plotdyhist(xlim, dat2, name2)
  plotdyhist(xlim, dat3, name3)
  plotdyhist(xlim, dat4, name4)
}

plotAge <- function(dat, name="max dy", threshold=c(0.4,0.8), oneRow = FALSE, exact = FALSE){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  for(i in 1:n){
    data2$maxdy[i] <- max(abs(data2$first.middle[i] - data2$middle.middle[i]), abs(data2$middle.middle[i] - data2$middle.last[i]))
  }
  #hist(data2$maxd, main=name, col="gray90")
  ages <- sort(data2$maxdy)
  
  if(exact){
    oldThresh <- threshold[2]
    medThresh <- threshold[1]
  } else {
    oldThresh <- ages[(n*threshold[2])]
    medThresh <- ages[(n*threshold[1])]  
  }
  
  for(i in 1:n){
    if(data2$maxdy[i] > oldThresh){
      data2$ageBin[i] <- "old"
    } else if(data2$maxdy[i] > medThresh){
      data2$ageBin[i] <-"medium"
    } else {
      data2$ageBin[i] <- "young"
    }
  }
  
  if(oneRow){par(mfrow=c(1,3))} 
  
  oldDat <- dat[(which(data2$ageBin=="old")+1),]
  plotThreeComparisons(oldDat, paste("old", name))

  medDat <- dat[(which(data2$ageBin=="medium")+1),]
  plotThreeComparisons(medDat, paste("medium", name))

  youngDat <- dat[(which(data2$ageBin=="young")+1),]
  plotThreeComparisons(youngDat, paste("young", name))
  
}

plotAge_helper <- function(dat, name="max dy", threshold=c(0.4,0.8), oneRow = FALSE, exact = FALSE){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  for(i in 1:n){
    data2$maxdy[i] <- max(abs(data2$first.middle[i] - data2$middle.middle[i]), abs(data2$middle.middle[i] - data2$middle.last[i]))
  }
  #hist(data2$maxd, main=name, col="gray90")
  ages <- sort(data2$maxdy)
  
  if(exact){
    oldThresh <- threshold[2]
    medThresh <- threshold[1]
  } else {
    oldThresh <- ages[(n*threshold[2])]
    medThresh <- ages[(n*threshold[1])]  
  }
  
  for(i in 1:n){
    if(data2$maxdy[i] > oldThresh){
      data2$ageBin[i] <- "old"
    } else if(data2$maxdy[i] > medThresh){
      data2$ageBin[i] <-"medium"
    } else {
      data2$ageBin[i] <- "young"
    }
  }
  
  if(oneRow){par(mfrow=c(1,3))} 
  
  oldDat <- dat[(which(data2$ageBin=="old")+1),]
  if(length(oldDat != 0)){
    plotThreeComparisons_helper(oldDat, paste("old", name))
  } else {
    xrange=c(0,3.2)
    yrange=c(0, .21)
    plot(xrange, yrange, type="n")
  }
  
  medDat <- dat[(which(data2$ageBin=="medium")+1),]
  if(length(medDat != 0)){
    plotThreeComparisons_helper(medDat, paste("medium", name))
  } else {
    xrange=c(0,3.2)
    yrange=c(0, .21)
    plot(xrange, yrange, type="n")
  }
    
  youngDat <- dat[(which(data2$ageBin=="young")+1),]
  if(length(youngDat != 0)){
    plotThreeComparisons_helper(youngDat, paste("young", name))
  } else {
    xrange=c(0,3.2)
    yrange=c(0, .21)
    plot(xrange, yrange, type="n")
  }

  # medDat <- dat[(which(data2$ageBin=="medium")+1),]
  # plotThreeComparisons_helper(medDat, paste("medium", name))
  # 
  # youngDat <- dat[(which(data2$ageBin=="young")+1),]
  # plotThreeComparisons_helper(youngDat, paste("young", name))
  
}

plotThreeComparisons_helper <- function(dat, name, xl = c(0.9, 3.2), yl=c(0,.21)){
  data2 <- dat[-c(1),]
  title <- name
  p=19
  n <- dim(data2)[1]
  cc <- rainbow(n)
  j <- runif(n, min=-0.2, max=0.2)
  inch <- 1/3
  
  #ylim = c(0,1.1*max(data2[,-c(10,11)]))
  plot(x=NULL, xlim=xl, ylim = yl, xaxt='n', ylab="genetic distance", main = title, xlab=NULL)
  
  with(data2, symbols(x=rep(1,n)+j, y=data2$first.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc, add=TRUE))
  
  with(data2, symbols(x=rep(2,n)+j, y=data2$middle.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(1,n)+j, y0=data2$first.middle, x1=rep(2,n)+j, y1=data2$middle.middle)
  
  with(data2, symbols(x=rep(3,n)+j, y=data2$last.middle, circles=sqrt(data2$size/pi), inches = inch, ann=FALSE, fg=NULL, bg=cc,  add=TRUE))
  segments(x0=rep(2,n)+j, y0=data2$middle.middle, x1=rep(3,n)+j, y1=data2$last.middle)
  #legend("topright", legend=c("1: first.first" ,"2: first.middle" ,"3: first.last","4: middle.middle" ,"5: middle.last" ,  "6: last.last"  ), lty=1:2, cex=0.8, bg="transparent")
  axis(side=1, at=1:3, labels = c("1: first.middle" ,"2: middle.middle" ,"3: middle.last"), las=0)
}


megaAgePlot <- function(dat1, name1, dat2, name2, dat3, name3, dat4, name4, threshold=c(0.2,0.8), exact=FALSE, dims = c(3,4)){
  par(mfcol=dims)
  plotAge_helper(dat1, name1, threshold = threshold, exact = exact)
  plotAge_helper(dat2, name2, threshold = threshold, exact = exact)
  plotAge_helper(dat3, name3, threshold = threshold, exact = exact)
  plotAge_helper(dat4, name4, threshold = threshold, exact = exact)
  
}

```



```{r}
plotGridGrid2 <- function(dat1, name1, dat2, name2, dat3, name3, dat4, name4, c1 = "#003153", c2 = "deepskyblue"){
  dat1 <- round(colMeans(dat1[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat2 <- round(colMeans(dat2[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat3 <- round(colMeans(dat3[-c(1), c(1:9)], na.rm = TRUE), 4)
  dat4 <- round(colMeans(dat4[-c(1), c(1:9)], na.rm = TRUE), 4)
  
  from <- c(rep("first", 3), rep("middle", 3), rep("last", 3))
  to <- c(rep(c("first", "middle", "last"), 3))
  
  rng <- range(dat1, dat2, dat3, dat4)
  
  lab <- "genetic\ndistance"
  
  tempavg1 <- matrix(dat1, nrow=9, byrow=TRUE)
  avg1 <- data.frame(tempavg1)
  colnames(avg1) <- "gen"
  avg1$from <- from
  avg1$to <- to
  
  tempavg2 <- matrix(dat2, nrow=9, byrow=TRUE)
  avg2 <- data.frame(tempavg2)
  colnames(avg2) <- "gen"
  avg2$from <- from
  avg2$to <- to
  
  tempavg3 <- matrix(dat3, nrow=9, byrow=TRUE)
  avg3 <- data.frame(tempavg3)
  colnames(avg3) <- "gen"
  avg3$from <- from
  avg3$to <- to
  
  tempavg4 <- matrix(dat4, nrow=9, byrow=TRUE)
  avg4 <- data.frame(tempavg4)
  colnames(avg4) <- "gen"
  avg4$from <- from
  avg4$to <- to
  
  color1 <- "#003153"
  color2 <- "deepskyblue"
  cc <- c(color1, color2)
  f <- 6
  
  q <- ggplot(data = avg1, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name1) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
  
  w <- ggplot(data = avg2, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name2) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
   
  e <- ggplot(data = avg3, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name3) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
  
   r <- ggplot(data = avg4, aes(x=factor(from, level=c("first", "middle", "last")), y=factor(to, level=c("last", "middle", "first")), fill=gen)) +     geom_tile() +    geom_shadowtext(aes(from, to, label = gen, color = "black"),color="white", bg.color="black", size = f) +    ggtitle(name4) +     scale_fill_gradientn(colors = cc, limits=rng) + xlab("") + ylab("")
   
  tiff("Plot1.1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(q)
  dev.off()
  
  tiff("Plot2.1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(w)
  dev.off()
  
  tiff("Plot3.1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(e)
  dev.off()
  
  tiff("Plot4.1.PNG", width = 5, height = 5, units = 'in', res = 300)
  print(r)
  dev.off()
  
}
```


## POSTER PLOTS ##
```{r}
plotGridGrid2(mauData1.688, "mauritania 1.688", melData1.688, "melanogaster 1.688",sechData1.688, "sechelia 1.688",simData1.688, "simulans 1.688")
plotGridGrid2(mauDataRsp, "mauritania Rsp", melDataRsp, "melanogaster Rsp",sechDataRsp, "sechelia Rsp",simDataRsp, "simulans Rsp")
```
```{r}
plotThreeComparisons(mauData1.688, "mauritania 1.688", yl=range(mauData1.688[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(melData1.688, "melanogaster 1.688", yl=range(melData1.688[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(simData1.688, "simulans 1.688", yl=range(simData1.688[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(sechData1.688, "sechelia 1.688", yl=range(sechData1.688[-c(1), c(1:9)]), xl=c(0.8,3.2))

plotThreeComparisons(mauDataRsp, "mauritania rsp", yl=range(mauDataRsp[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(melDataRsp, "melanogaster rsp", yl=range(melDataRsp[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(simDataRsp, "simulans rsp", yl=range(simDataRsp[-c(1), c(1:9)]), xl=c(0.8,3.2))
plotThreeComparisons(sechDataRsp, "sechelia rsp", yl=range(sechDataRsp[-c(1), c(1:9)]), xl=c(0.8,3.2))
```


```{r}
x <- c(0.8, 3.2)
x <- c(0.8, 3.8)
y <- c(0, 1.16)

png("sim1688Three_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(simData1.688, "simulans 1.688", xl=x, yl=y)
dev.off()

png("mau1688Three_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(mauData1.688, "mauritiana 1.688", xl=x, yl=y)
dev.off()

png("sech1688Three_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(sechData1.688, "sechellia 1.688", xl=x, yl=y)
dev.off()

png("mel1688Three_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(melData1.688, "melanogaster 1.688", xl=x, yl=y)
dev.off()

png("simRspThree_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(simDataRsp, "simulans Rsp", xl=x, yl=y)
dev.off()

png("mauRspThree_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(mauDataRsp, "mauritania Rsp", xl=x, yl=y)
dev.off()

png("sechRspThree_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(sechDataRsp, "sechellia Rsp", xl=x, yl=y)
dev.off()

png("melRspThree_v3.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(melDataRsp, "melanogaster Rsp", xl=x, yl=y)
dev.off()
```

```{r}
tiff("sim1688Three2.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(simData1.688, "simulans 1.688", xl=c(0.8, 3.2), yl=c(0,1.1))
dev.off()

tiff("mau1688Three2.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(mauData1.688, "mauritiana 1.688", xl=c(0.8, 3.2), yl=c(0,1.16))
dev.off()

tiff("simRspThree2.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(simDataRsp, "simulans Rsp", xl=c(0.8, 3.2), yl=c(0,1.16))
dev.off()

tiff("mauRspThree2.png",width=6,height=4.5,units="in",res=300)
plotThreeComparisons(mauDataRsp, "mauritania Rsp", xl=c(0.8, 3.2), yl=c(0,1.16))
dev.off()
```
plotAllComparisons(simData1.688, "simulans 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
tiff("sech1688six.png",width=6,height=4.5,units="in",res=300)
plotAllComparisons(sechData1.688, "sechelia 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
plotAllComparisons(melData1.688, "melanogaster 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
plotAllComparisons(mauData1.688, "mauritania 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))


## 1.688 plots ##
```{r}
tiff("sim1688six.png",width=6,height=4.5,units="in",res=300)
plotAllComparisons(simData1.688, "simulans 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
dev.off()

tiff("sech1688six.png",width=6,height=4.5,units="in",res=300)
plotAllComparisons(sechData1.688, "sechelia 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
dev.off()

tiff("mel1688six.png",width=6,height=4.5,units="in",res=300)
plotAllComparisons(melData1.688, "melanogaster 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
dev.off()

tiff("mau1688six.png",width=6,height=4.5,units="in",res=300)
plotAllComparisons(mauData1.688, "mauritania 1.688", xl=c(0.8, 6.2), yl=c(0,1.16))
dev.off()

``` 

```{r}
plotAllComparisons(simData1.688, "sim x 1.688 q1 q1 f4", xl=c(0.8, 6.2), yl=c(0,1.16))
plotAllComparisons(sechData1.688, "sech x 1.688 q1 q1 f4", xl=c(0.8, 6.2), yl=c(0,1.16))
plotAllComparisons(melData1.688, "mel x 1.688 q1 q1 f4", xl=c(0.8, 6.2), yl=c(0,1.16))
plotAllComparisons(mauData1.688, "mau x 1.688 q1 q1 f4", xl=c(0.8, 6.2), yl=c(0,1.16))
``` 

## rsp plots ##
```{r}
mauData <- read.table("dmau_QM_q20_q80_f3_03.txt", header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE)
simData <- read.table("dsim_QM_q20_q80_f3_03.txt", header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE)
sechData <- read.table("dsech_QM_q20_q80_f3_03.txt", header = TRUE, sep = "\t",strip.white=TRUE,stringsAsFactors=FALSE)
melData <- read.table("dmel_QM_q20_q80_f3.txt_03", header = TRUE, sep = "\t",strip.white=TRUE,stringsAsFactors=FALSE)

cow1 <- plotGrid(mauData, "mau rsp x 20%/80% f3")
cow2 <- plotGrid(simData, "sim rsp x 20%/80% f3")
cow3 <- plotGrid(sechData, "sech rsp x 20%/80% f3")
cow4 <- plotGrid(melData, "mel rsp x 20%/80% f3")
plotGridGrid(cow1, cow2, cow3, cow4)


plotAllComparisons(simData, "sim x rsp 20% 80% f3")
plotAllComparisons(sechData, "sech x rsp 20% 80% f3")
plotAllComparisons(melData, "mel x rsp 20% 80% f3")
plotAllComparisons(mauData, "mau x rsp 20% 80% f3")


plotThreeComparisons(simData, "sim x rsp 20% 80% f3")
plotThreeComparisons(sechData, "sech x rsp 20% 80% f3")
plotThreeComparisons(melData, "mel x rsp 20% 80% f3")
plotThreeComparisons(mauData, "mau x rsp 20% 80% f3")

plotdyhists(c(0, .21), simData, "sim x rsp 20% 80% f3", sechData, "sech x rsp 20% 80% f3", melData, "mel x rsp 20% 80% f3", mauData, "mau x rsp 20% 80% f3")
```

thoughts: i should probably get the youngest first, then the middle, then the old so that I have data to subset? I need a better way of subsetting data so that there's no null pointers. Also, need to put a % filter AND an exact filter on what counts as old, so that I can compare between species. 

## PLOTTING AGE ##
```{r}
plotAge(melData, "mel x 1.688 15% 85% f3")
megaAgePlot(melData, "mel x 1.688 15% 85% f3", sechData, "sech x 1.688 15% 85% f3", simData, "sim x 1.688 15% 85% f3",  mauData, "mau x 1.688 15% 85% f3", c(0.2, 0.8))

megaAgePlot(melData, "mel x 1.688 15% 85% f3", sechData, "sech x 1.688 15% 85% f3", simData, "sim x 1.688 15% 85% f3",  mauData, "mau x 1.688 15% 85% f3", threshold = c(0.01, 0.03), exact=TRUE)

# plot rsp vs 1.688
sechData1688 <- read.table("dsech_x_1.688_q15_q85_f3_01.txt", header = TRUE, sep = "\t", strip.white=TRUE, stringsAsFactors=FALSE)
sechDataRSP <- read.table("dsech_QM_q20_q80_f3_03.txt", header = TRUE, sep = "\t",strip.white=TRUE,stringsAsFactors=FALSE)
megaAgePlot(dims = c(3,2), dat1 = sechData1688, name1 =  "dsech_x_1.688_q15_q85_f3_01.txt", dat2 = sechDataRSP, name2 = "dsech_QM_q20_q80_f3_03.txt", dat3 = sechData1688, name3 =  "dsech_x_1.688_q15_q85_f3_01.txt", dat4 = sechDataRSP, name4 = "dsech_QM_q20_q80_f3_03.txt",  threshold = c(0.01, 0.03), exact=TRUE)
```




```{r}
melrspDist <- read.table("maps_and_stuff//dmel_rsp_dist.tsv", header = TRUE, sep="\t", row.names = 1)
maurspDist <- read.table("maps_and_stuff//dmau_rsp_dist.tsv", header = TRUE, sep="\t", row.names = 1)
simrspDist <- read.table("maps_and_stuff//dsim_rsp_dist.tsv", header = TRUE, sep="\t", row.names = 1)
sechrspDist <- read.table("maps_and_stuff//dsech_rsp_dist.tsv", header = TRUE, sep="\t", row.names = 1)

mel1688Dist <- read.table("maps_and_stuff//dmel_1.688_dist.tsv", header = TRUE, sep="\t", row.names = 1)
mau1688Dist <- read.table("maps_and_stuff//dmau_1.688_dist.tsv", header = TRUE, sep="\t", row.names = 1)
sim1688Dist <- read.table("maps_and_stuff//dsim_1.688_dist.tsv", header = TRUE, sep="\t", row.names = 1)
sech1688Dist <- read.table("maps_and_stuff//dsech_1.688_dist.tsv", header = TRUE, sep="\t", row.names = 1)

melrspClust <- read.table("maps_and_stuff//dmel_rsp_clust.tsv", header=FALSE, sep="\t")
maurspClust <- read.table("maps_and_stuff//dmau_rsp_clust.tsv", header=FALSE, sep="\t")
simrspClust <- read.table("maps_and_stuff//dsim_rsp_clust.tsv", header=FALSE, sep="\t")
sechrspClust <- read.table("maps_and_stuff//dsech_rsp_clust.tsv", header=FALSE, sep="\t")

mel1688Clust <- read.table("maps_and_stuff//dmel_1.688_clust.tsv", header=FALSE, sep="\t")
mau1688Clust <- read.table("maps_and_stuff//dmau_1.688_clust.tsv", header=FALSE, sep="\t")
sim1688Clust <- read.table("maps_and_stuff//dsim_1.688_clust.tsv", header=FALSE, sep="\t")
sech1688Clust <- read.table("maps_and_stuff//dsech_1.688_clust.tsv", header=FALSE, sep="\t")

#takes the distance matrix, the start coordinate of the first monomer, and the end coordinate of the last monomer
plotHeatMap <- function(dat, start, end){
  library("ggplot2")
  library("reshape2")
  
  keys <- row.names(dat)
  coords <- as.numeric(substring(keys, 3, regexpr("-", keys)-1))
  startIndex <- 1
  endIndex <- 1
  while(start > coords[startIndex]){ startIndex <- startIndex + 1}
  while(end > coords[endIndex+1]){ endIndex <- endIndex + 1}
  mydata <- dat[startIndex:endIndex, startIndex:endIndex]
  #return(mydata)
  
  cormat <- round(cor(mydata),2)
  melted_cormat <- melt(cormat)
  print(ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + geom_tile())
}

plotAllArrays <- function(dist, clust){
  for(i in 1:(nrow(clust)-1) ){
    plotHeatMap(dist, clust$V8[i], clust$V11[i])
  }
}

# plotHeatMap(mel1688Dist, 2426474, 2427088)
# plotHeatMap(mel1688Dist, 8698963, 8702559)
# plotHeatMap(mel1688Dist, 12794971, 12797970)
# plotHeatMap(mel1688Dist, 2114248, 2119890)

plotAllArrays(mel1688Dist, mel1688Clust)

for(i in 1:(nrow(maurspClust)-1)){
  plotHeatMap(maurspDist, maurspClust$V8[i], as.numeric(maurspClust$V11[i]))
}

```





